---
title: "Analysis of Sleep Data"
description: |
  Welcome to the website. I hope you enjoy it!
site: distill::distill_website
---

First, let's see how many times I slept before 10pm. I always make an effort to sleep before 10pm, as I strive to obtain a good health.



```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(gridExtra)
library(ggpubr)
library(ggplot2)
library(gganimate)
library(plotly)


data <- read_csv("/Applications/sleep.csv")
```


```{r, echo = FALSE}
data1 <- data

data1 <- data1%>%
  mutate("minutes" = hour(data1$sleep_hr)*60 + minute(data1$sleep_hr))%>%
  mutate(over10 = if_else(minutes < 470.0, TRUE, FALSE))
data1%>%
  group_by(over10)%>%
  summarize(total = n())%>%
  ggplot(aes(x = over10, y = total))+
  geom_histogram(fill = "hot pink", stat = "identity")+
  geom_text(aes(label = total, y=total + 2.5)) + 
  theme(panel.background = element_rect(fill="white"))+
  theme(panel.grid.major = element_blank()) + 
  scale_x_discrete(labels = c('Yes', "No")) + 
  labs(x = "Did I Sleep Before 10pm?", y = "Number of Occurences", title = "How Many Times Did I Sleep Before 10pm in Semester 1 of Junior Year?")
  
```
<aside>

I slept before 10pm on nearly 84% of my school days

</aside>


I was also curious to know which days of the week I would tend to sleep past 10pm the most.


```{r, echo = FALSE}
data1$day_of_week <- factor(data1$day_of_week, levels = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday"))
data1 <- data1%>%
  group_by(day_of_week)%>%
  mutate(past10 = sum(over10 == TRUE))
data1%>%
  ggplot(aes(x = day_of_week, y = past10, color = day_of_week)) + 
  geom_point(stat ="identity", size = 5) + 
  theme(legend.position = "none") + 
  theme(panel.grid.major = element_line(color = "gray", size = 0.05)) + 
  theme(panel.background = element_blank()) + 
  theme(axis.title.x = element_text(size = 11)) +
  theme(axis.text.y.left = element_text(size = 10)) +
  labs(x = "Day of Week", y = "Number of Occurences", title = "How Many Times Each Day of the Week Did I Sleep Past 10pm?")
  
```
<aside>

Sundays tended to be I would sleep past 10pm the most, partly due to late-night events that took place then.

</aside>


But, let's see what day of the week I would sleep the most on.

```{r}
total_sleep <- data
total_sleep$day_of_week <- factor(total_sleep$day_of_week, levels = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday"))
total_sleep <- total_sleep%>%
  mutate("minutes" = hour(data1$sleep_hr)*60 + minute(data1$sleep_hr))
total_sleep <- aggregate(total_sleep$minutes, by = list(total_sleep$day_of_week), FUN=mean)
total_sleep%>%
  rename(day_of_week = "Group.1", minutes = "x")%>%
  ggplot(aes(x = day_of_week, y = minutes, fill = day_of_week)) + 
  geom_histogram(stat = "identity") +
  coord_cartesian(ylim = c(475, 500)) + 
  geom_text(aes(label = round(minutes, digits = 1), vjust = -0.9)) + 
  theme(legend.position = "none", panel.background = element_blank()) + 
  labs(x = "Day of Week", y = "Minutes of Sleep", title = "Average Minutes of Sleep By Day of Week")
```

<aside>

According to the graph, I slept the most on Tuesdays, while I slept the least on Sundays.

</aside>


I was even curious to know which month I slept the most in.


```{r}
month_data <- data
month_data$date <- as.Date(month_data$date, "%m/%d/%Y")
month_data <- month_data%>%
  mutate(month = month(month_data$date))%>%
  mutate("minutes" = hour(data$sleep_hr)*60 + minute(data$sleep_hr))
month_data <- aggregate(month_data$minutes, by = list(month_data$month), FUN = mean)
month_data%>%
  rename(month = "Group.1", min = "x")%>%
  ggplot(aes(x = month, y = min, fill = month))+
  geom_bar(stat = "identity")+
  coord_cartesian(ylim = c(475, 500)) + 
  theme(panel.background = element_blank(), panel.grid = element_blank(),legend.position = "none") +
  geom_text(aes(label = round(min, digits = 1), vjust = -0.9)) + 
  labs(x = "Month Number", y = "Minutes", titlee = "Average Minutes of Sleep By Month")

```


<aside>

I slept the most in November, while I slept the least in December (partly because of studying for finals)

</aside>


Here is an overall line graph representing the times I went to bed before each school day. 
NOTE: data is not included for ALL dates because I only kept track of my sleep times before school days. 

```{r fig.width=30, fig.height=20}
data$date <- as.Date(data$date, "%m/%d/%Y")
data$time_pm <- as.POSIXct(data$time_pm)
graph <- data%>%
  select(date, time_pm, sleep_hr)%>%
  ggplot(aes(x = date, y = time_pm))+
  geom_line(group = 1, color = "red", size = 2) + 
  geom_point(size = 5) +
  theme(axis.text.x = element_text(size = 50, angle = 45, hjust = 1), axis.text.y = element_text(size = 40), panel.background = element_blank(), axis.title = element_text(size = 35), plot.title = element_text(size = 50, color = "red"))+
  scale_y_datetime(date_labels = "%I:%M:%S %p") +
  geom_vline(xintercept = as.Date(c("0021-09-01", "0021-10-01", "0021-11-01", "0021-12-01"))) +
  labs(x = "Month", y = "Time Slept", title = expression(underline("Trend of Sleeping Times")))
graph
```


Overall, through this fun project, I was able to visualize my own data about my sleep for semester 1 of junior year. 

